Measurement of the positive kaon-argon total hadronic differential cross section in the LArIAT experiment

### 2018-03-13 Drafting.tex
s

\section{Non-LArTPC Instruments}\label{sec:FTBF}
The Fermilab Test Beam Facility (FTBF) receives a 120~GeV$/c$ primary proton beam with variable intensity, split by electrostatic septa from beam circulating in the Main Injector. Each supercycle of the Fermilab accelerator complex, roughly 60 seconds in duration, includes a four-second "spill" of primary beam to FTBF. Primary beam is sent to either or both of two experimental halls, named Meson Test and Meson Center.

The LArIAT experiment utilized the Meson Center beam line and had this primary beam focused onto a tungsten target. The resulting secondary charged particle beam is selected to have peak momentum between 8-80\,GeV$/c$ and is transported to the LArIAT experimental hall, designated MC7, where it is focused onto a copper target. This target, and the steel collimator hosting it, form the beginning of the tertiary particle beam and the LArIAT apparatus shown in  Fig.~\ref{fig:tert-layout}.  For most of the LArIAT data taking this secondary beam peak momentum was fixed at 64~GeV$/c$, although some lower secondary beam momentum settings were explored.  With such an energetic secondary beam on it, the copper target produces a tertiary beam which is comprised of mostly pions and protons with a small fraction of electrons, muons, and kaons present as well.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{LArIAT Tertiary Beam}\label{sec:TertiaryBeam}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The tertiary beam consists of a target and collimator system and two bending magnets in a similar configuration used for the  MINERvA T-977 test beam calibration~\cite{MinervaTestbeam}. A set of four wire chambers and two time-of-flight scintillating paddles, also shown in Fig.~\ref{fig:tert-layout}, provide tracking, momentum determination, and particle identification (PID).

The geometry of the tertiary beam line in MC7 has been optimized for LArIAT.  A $13^\circ$ production angle at the target and its enclosing collimator, as well as a $10^\circ$ bend through a pair of dipole magnets provide particle momenta spectra tunable in the range from 0.2 to 2.0~GeV/c, as a function of the field intensity in the magnets.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=5.3in]{figures/LArIATBeamline.png}
\caption{
{\scriptsize \sf The tertiary beam line layout. Upstream and downstream collimators are in gray, bending magnets in yellow, wire chambers are in red, and the liquid argon TPC volume in green.}
}
\label{fig:tert-layout}
\end{centering}
\end{figure}

In the subsequent sections, we will detail the various subsystems installed along the beamline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Time-of-Flight System}\label{sec:TOF}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The LArIAT time-of-flight (TOF) detector system consists broadly consists of two scintillator paddles, which bracket the beamline and are shown in blue in Figure~\ref{fig:tert-layout}. The exact details of the of the TOF system were changed between Run-II and Run-III to allow for better performance and timing resolution.

\paragraph{\textbf{TOF System for Run-I and Run-II:}}
The upstream paddle, shown in Figure \ref{}, has a relatively small active area (10~cm x 6~cm ) and was chosen to be a relatively thin piece of scintillator to minimize any impact on the momentum of the particles coming from the target. Light guides were mounted on all four edges which lead to two \textit{insert PMT type} PMTs mounted on the beam left side. The downstream paddle, shown in Figure \ref{fig:TOFSystemRunIandII}, was chosen to have a slightly larger area (14~cm x 14~cm) and had two \textit{insert PMT type} PMTs which were read out on opposite ends of the paddle.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
%\includegraphics[height=2.3in]{figures/tofdelay.png}
\caption{
{\scriptsize \sf Pictures of the TOF system as was deployed during Run-I and Run-II data taking. The left image is of the upstream TOF paddle and the right image is of the downstream TOF paddle }
}
\label{fig:TOFSystemRunIandII}
\end{centering}
\end{figure}

\paragraph{\textbf{TOF System for Run-III:}}
Two modifications were made to the downstream TOF paddle for Run-III to improve the efficiency and timing of the system. The large area scintillator paddle was replaced with a slightly smaller paddle more similar to the upstream and was now readout with four new PMT's (2" Hamamatsu PMTs (R-1828) inherited from the muon g-2 experiment(E821) at BNL) located on the diagonals of the counter, as shown in Figure \ref{fig:TOFSystemRunIII}.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{figures/TOFRunIII.png}
\caption{
{\scriptsize \sf Image of the modified downstream TOF system deployed during Run-III data taking }
}
\label{fig:TOFSystemRunIII}
\end{centering}
\end{figure}

%The active area of the upstream paddle is relatively small ( 10~cm x 6~cm ) and that of the downstream paddle is somewhat larger ( 14~cmx 14~cm ). Lightguides are mounted on all four edges of each paddle. In the first two LARIAT production runs, each of the paddles was read out by two (xxkxkxkxk) photomultiplier tubes (PMTs), The long axis of the downstream paddle was directed horizontally and read out at either end. The upstream paddle was rotated by 45 degrees with respect to the horizontal and its two PMTs were mounted to the left side. In run 3, four more PMTs were added to the system. The upstream paddle was read out with the original set of PMTs and the downstream paddle with four 2" Hamamatsu PMTs (R-1828) inherited from the muon g-2 experiment(E821) at BNL.

During data-taking cycles, signals from the TOF PMTs were sampled at 1 GHz
with a CAEN 1751 digitizer and 12 bit samples were stored in a circular memory buffer. In response to an experimental trigger, a 28.7 $\mu$ second window of samples, starting approximately 8.4 $\mu$sec before the trigger, was written to the
output. The amplitude of the TOF signals was typically 200 mV in the upstream TOF PMTs but only 50 mV in those of the downstream counter. The signals have a rise time (10-90\%) of 4 ns and a full width, half-maximum of 9 ns. The rate in the upstream counter was typically 15 kHz and much less, 400 Hz in the downstream counter.

Because the shape of signals from each TOF PMT was highly uniform, the time of the pulses was determined using an oversampled template derived from the data itself. The DC offset (pulse pedestal) is taken from samples far from the pulse, The template is stretched vertically to match the pedestal-subtracted pulse amplitude and moved horizontally to match the time. The pulse time-pickoff resolution is better than 100 ps and relative amplitude resolution is better than x\%. Since the average rate of pulses incident on the ToF system is modest, pulse pile up is not a significant problem. Given the uniform width of the pulses produced by any given PMT (sigma of 400 ps), the pulse width can be used to flag events where two pulses overlap closely in time. Simulations indicate that for pulses as close as 4 ns, a well-chosen pulse width cut is 90\% efficient.

To determine the particles' time of arrival, pulse times from the multiple PMTs mounted on each paddle had to be combined. During Run-I and II, with two PMTs mounted on each paddle, a simple average was used. In the case of the downstream paddle, with PMTs mounted at opposite ends, the average corrected for the fact that transit time to the two PMTs depended on the particle's point of impact on the scintillator. A plot of the time of arrival {\it difference} between the two downstream PMTs vs the longitudinal impact point, made with the help of track stubs from the wire chamber system, is shown in Fig.~\ref{fig:tofdelay}. As expected, the time difference
changes systematically across the face of the scintillator.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
%\includegraphics[height=2.3in]{figures/tofdelay.png}
\caption{
{\scriptsize \sf $\Delta-t$ between times registered on two downstream paddles.}
}
\label{fig:tofdelay}
\end{centering}
\end{figure}

Taking the average minimizes ToF errors arising from optical path differences in the scintillator, However, even for a set of particles which pass through a single small area of the paddle, the times of pulses registered in the two PMTs are still spread by approximately 300~ps, an uncertainty which is probably caused by transit time jitter in the PMTs themselves. This jitter is evident in both the upstream and downstream detectors.

Although climate-control in the LArIAT experiment hall is fairly primitive, there is little sign of systematic timing drift over longer periods. The average time differences between pairs of PMTs reading out the same scintillator varied by no more than 150~ps over the 3-4 months of a data-taking period.

Finally, the amplitude of the ToF pulses (peak minus pedestal) reflects the energy deposited in the scintillator, largely through ionization.  At a given momentum, more massive particles such deuterons, protons, and kaons, will deposit more energy than less massive particles, such as electrons, muons, and pions. As described below, ToF and momentum information from the wire chambers can be combined to determine the particle's mass and hence its identity. Although the energy deposited in the scintillator isn't used to distinguish among the various particle types, it's clear from Figure~\ref{fig:tofamplitude} that the spectra of energy deposition for
electrons, pions, and protons are very different.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
%\includegraphics[height=2.3in]{figures/tofamplitude.png}
\caption{
{\scriptsize \sf Average upstream ToF pulse amplitude for protons and pions/positrons.}
}
\label{fig:tofamplitude}
\end{centering}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Bending Magnets}\label{sec:Magnets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The pair of spectrometer magnets in the LArIAT tertiary beam are Fermilab type "NDB" electromagnets, originally used in the anti-proton ring. These magnets provide the necessary bend in the particle trajectory to allow for a momentum measurement to be performed.  The magnets have a gap height of 14.224~cm, a gap width of 31.75~cm, and have an iron length of 46.67~cm.  The aperture presented by the magnets is larger than that of the wire chambers ($\sim$12.5cm) and thus only the central part of the magnet is ever utilized.  Over this limited aperture there is negligible variation of the field integral and thus a very uniform field is provided. The field intensity in one of the pair of magnets was measured using two Hall probes, both calibrated with NMR, to obtain the excitation curve shown in Figure~\ref{fig:magnet_excitation}). The second magnet, having been made to the same standard and having the same history, is assumed to have a very similar response.
\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=3.0in]{figures/ExcitationCurves.png}
\caption{
{\scriptsize \sf Excitation Curve, B/I vs. I, for one NDB magnet, using two Hall probes (blue and green). Parameters from a cubic fit (black curve) to average of measurements (red) given in legend.}
}
\label{fig:magnet_excitation}
\end{centering}
\end{figure}

These magnets were air- and water-cooled during operations and their temperatures monitored. Due to concerns of overheating, the maximum usable field at the center of the magnets is $\sim$0.35 Tesla with 100 Amps of current being passed through the magnets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Multi-Wire Proportional Chambers}\label{sec:MWPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The wire chambers are based on the Fenker Chambers~\cite{Fenker} long in use at Fermilab.  The chambers have been upgraded by adding additional grounding to improve the signal to noise in the electronic readout.  The chambers, shown in Figure~\ref{fig:wirechamber}, have an effective aperture of 128~mm in both horizontal and vertical distances.  The wires are spaced at 1~mm, with 128 wires in each view.  In a test beam, the chambers have typical efficiencies of 98\% to 99\%. The gas used is 85\% Argon + 15\% isobutane.  The wire chambers typically operate between 2400 and 2500 volts.

\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{figures/WireChamber.png}
\caption{
{\scriptsize \sf Image of one of the wire chambers used in the LArIAT tertiary beamline.}
}
\label{fig:wirechamber}
\end{centering}
\end{figure}

The front end amplifier/discriminator uses the ASDQ chip~\cite{ASDQchip}. Two of the ASDQ chips are mounted on a mother board that is plugged into the chamber.  Short flat cables are used to connect these ASDQ mother board to a new, multi-hit TDC~\cite{Sten}. This TDC provides a (maskable) fast OR output that can be used in a first level trigger.

This TDC can accept multiple hits per wire with a time resolution of 1.18~ns/bin.  The TDCs can accept 2 edges per 9~ns.  The maximum event rate that can be accepted by the chamber system is of the order of one megahertz.  These limitations are clearly not an issue for the LArIAT beamline where the rates and timing resolution required are much less stringent than this.  There is enough memory on the TDC board to buffer a full spill of data (up to about 100 events/spill).  As in this application the spills occur only once per minute, there is ample time to read out the whole spill through a controller specially designed to support these TDCs.  Power and data flow to and from the controller to the TDCs and from the controller to the rest of the DAQ is via LVDS.  The time window for acceptance for hits, time offsets, front end threshold, and pulse shaping parameters may be programmed through the controller via a USB link from a PC or through an Ethernet connection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Aerogel Cherenkov Detectors}\label{sec:Aerogel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Aerogel is an ultra-light material in which the liquid component of the gel has been replaced with a gas. The result is a solid with extremely low density, low thermal conductivity, and low index of refraction. The goal of having an aerogel threshold Cherenkov detector in the LArIAT beam line is to separate muons and pions in the momentum range where muons emit Cherenkov radiation while pions do not. This technique was demonstrated by the MICE and Belle II experiments ~\cite{MICE-aerogel,BelleII-aerogel} and in LArIAT we use two aerogel threshold Cherenkov detector with index of refraction of 1.057 and 1.103. Having different indices of aerogel allows LArIAT to do this separation in two different momentum ranges of interest.

\begin{figure}[htb]
\centering
\includegraphics[height=1.85in]{figures/Aerogel1103Figure.png}
\hspace{1cm}
\includegraphics[height=1.85in]{figures/Aerogel1057Figure.png}
\caption{Number of photoelectrons per cm versus momentum for the two indices of refraction that are employed by the LArIAT aerogel detectors. The photoelectron yield includes the response of a bialkali photocathode following the recipe in ~\cite{bib8}. }
\end{figure}

%%% KEK couter
The Aerogel Threshold Cherenkov Detector with the refractive index of 1.103 is placed just behind the second collimator on the tertiary beam line, between the two downstream wire chambers.
Figure~\ref{fig:kek_aerogel} is a picture of this aerogel detector.
It consists of 7 aerogel tiles (totaling 110 mm long in the beam direction), and the cross section of the detector is 108 mm $\times$ 108 mm.
The array of the aerogel tiles is wrapped with a diffusion sheet and viewed by two PMTs (HAMAMATSU R329-02) from the sides.
Figure~\ref{fig:kek_aerogel_ly} shows the observed light yield distribution for 550-800~MeV pions hitting the middle of the detector.
The obtained light yield is equivalent to 22 photoelectrons for $\beta=1$.
The fake rate for particles with velocity below the Cherenkov threshold is measured to be around 0.5\% with the threshold of 1.5 photoelectrons.

\begin{figure}[htb]
\centering
\includegraphics[height=1.85in]{figures/kek_aerogel.jpg}
\caption{The Aerogel Threshold Cherenkov Detector with the refractive index of 1.103.}
\label{fig:kek_aerogel}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[height=1.85in]{figures/kek_aerogel_ly.png}
\caption{The observed light yield distribution for 550-800 MeV pions hitting the middle of the detector.
The obtained light yield is equivalent to 22 photoelectrons for $\beta=1$.}
\label{fig:kek_aerogel_ly}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Punch-Through and Muon Range Stack Instruments}\label{sec:MuRS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{muon-Punch.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{LArIAT Cosmic Ray Paddle Detectors}\label{sec:CosmicRayPaddle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

LArIAT's system to trigger on cosmic rays is based on two so-called "cosmic towers" which stand  upstream and downstream of the cryostat, one on beam's right and one on beam's left, framing the cryostat.  Each cosmic tower is composed of two paddle assemblies, upper and lower.  The paddle assemblies each consist of four paddles, a matched pair which stand upright and a second matched pair lying across the top  of the assembly, to act as a veto for downward-going cosmic ray air showers.  Unless vetoes by the horizontal paddles, signals from paddle assemblies along the body diagonals of the TPC are combined in a logical ``AND'' to select cosmic muons crossing the TPC along one of its diagonals. A high proportion of events triggered this way contain cosmic ray tracks crossing both anode and cathode.  Such tracks provide a sample of LAr ionization with effectively uniform linear ionization density, but experience the entire range of charge attenuation available in the TPC before they drift to the anode. These tracks are used to calculate and monitor the level of electronegative contaminants in the liquid argon and provide a calibration sample for calorimetry and electric field studies outlined in Section \ref{sec:DetectorPerformance}.

The paddles have trapezoidal shape and are each enclosed in an aluminum case. An example is shown in Fig. \ref{pic:cosmicpaddle}. They come in two different sizes: a smaller version, with bases $32.2~cm$ and $26.7~cm$, $61.0~cm$ height and $3.02~cm$ thickness, and a bigger version, with bases $33.2~cm$ and $27.0~cm$, $70.8~cm$ height and $3.02~cm$ thickness. Each paddle is equipped with wavelength-shifting optical fibers running along one of the long sides and optically coupled to a low voltage, Zener-diode Hamamatsu H5783 PMT.  Signals from the PMT are amplified and discriminated by a custom-made PMT Amplifier and Discrimination (PAD) circuit mounted at one end of the paddle, then sent through a CAT5 cable to a Control and Concentrator Unit (CCU) which both power the PMT, controlling voltage and threshold, and output the PMT signal as logic ECL pulse.

\begin{figure}[h!]
 \centering
 \includegraphics[angle=90,width=0.7\textwidth]{figures/Cosmic_Paddle.jpg}
\caption{
Photograph of one of the scintillation counters used in the cosmic towers. 
} 
\label{pic:cosmicpaddle}
\end{figure}

The paddles were selected from a pool of over 300 scintillating counters collected during the decommissioning of the CDF detector at Fermilab. 
For each counter, both the efficiency $\varepsilon_P$ and the noise $\eta_P$ as a function of the voltage were determined. The measurement was performed sandwiching the given paddle among 4 sample counters, placed two above and two below the paddle under test. The efficiency 
$\varepsilon_P$ was defined as the ratio between the 5-fold coincidence and the 4-fold coincidence of the sample counters. The accidental rate $\eta_P$ was instead defined as the number of 5-fold coincidence observed during ten minutes of data acquisition, when the signal of the paddle under test was delayed by $5 \mu s$. Each paddle with $\varepsilon_P \geq 95\%$ and $\eta_P = 0$ at working voltage was identified as a candidate for the Cosmic Ray system. The ones with the highest efficiency and lowest single count rate were then selected to realize the system itself. 
The plot of $\varepsilon_P$ as a function of the PMT voltage for one example paddle is shown in Fig. \ref{pic:CR_Effplot}.

\begin{figure}[h!]
 \centering
 \includegraphics[width=0.7\textwidth]{figures/TSU29_Efficiency.png}
\caption{
Plot of the counter efficiency $\varepsilon_P$ as a function of the PMT voltage for one of the paddles composing the Cosmic Ray system. 
} 
\label{pic:CR_Effplot}
\end{figure}

%$\varepsilon_P$ at a given voltage is defined as:

%$$
%\varepsilon_P = \frac{R_{1-2} \land R_{3-4} \land R_P}{R_{1-2} \land R_{3-4}}
%$$

%where $R_P$ is the rate of the paddle $P$ to be tested, $R_{1-2}$ is the coincidence rate of two sample paddles positioned above $P$, while $R_{3-4}$ is the coincidence rate of two sample paddles positioned below $P$.
%$\eta_P$ at a given voltage is instead defined as:

%$$
%\eta_P = \frac{R_{1-2} \land R_{3-4} \land R_{P^*}}{R_{1-2} \land R_{3-4}}
%$$

%where $R_{P^*}$ is the Rate of the paddle $P$

The trigger rate $R$ of the whole system is $R=0.032Hz$, corresponding to $\sim 1.9~\mu/minute$.

\section{The LArIAT Detector}\label{sec:LArIATDetector}

An Intro paragraph, as Will F. suggested, would be good here at the start of section 3. I might also rename this section to ?The LArIAT LArTPC Detector?, since beam line stuff is also ?The LArIAT Detector?.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cryogenics}\label{sec:Cryo}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{CryoDetails.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Projection Chamber}\label{sec:TPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{TPCDetails.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TPC Electronics}\label{sec:MSUElectronics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{TPCelectronics.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Digitization}\label{sec:Digitization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Digitization.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Trigger and Readout System}\label{sec:Trigger}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Trigger.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photon Detection System}\label{sec:PhotonSystem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{LightDetectionSystem.tex}

The LArIAT cryogenic system consists of the repurposed ArgoNeuT cryostat, the new process piping, and a liquid argon filtration system installed at Fermilab's Test Beam Facility.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}{Cryostat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The LArIAT cryostat, shown in Figure \ref{fig:LArIATCryoStat}, was repurposed from the ArgoNeuT experiment with a series of modifications to allow for operations in a charged particle test beam. The cryostat \cite{ArgoNeuT} consists of an inner volume containing the purified liquid argon and an outer volume serving as a vacuum jacket with layers of aluminized mylar superinsulation. Both the inner and outer cryostat vessels are cylindrical in shape with convex end caps.  Access to the internal volume is possible by opening the upstream end caps of the inner and outer vessels. The main axis of the cryostat is horizontal and oriented parallel to the beam. The inner vessel is 76.2~cm in diameter and 130~cm in length, corresponding to a liquid argon volume of about 550~L, or a mass of 0.76 t. The cryostat has a wide neck, or ``chimney'', protruding from its top at mid-length which serves as an access path for signal cables from the LArTPC and the internal instrumentation, as well as for the high voltage feedthrough.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.18]{./figures/Cryostat1.jpg}
\includegraphics[scale=0.07]{./figures/Cryostat2.jpg}
\caption{\emph{(left)} The LArIAT cryostat open with the TPC placed in the inner volume. \emph{(right)} The LArIAT cryostat fully sealed during initial commissioning prior to installation at Fermilab Testbeam Facility.}
\label{fig:LArIATCryoStat}
\end{figure}

Several modifications to the cryostat were made to meet the requirements of operating in a charged particle test beam and to facilitate the new liquid argon purification system. These modifications, shown in Figure \ref{fig:LArIATCryoMods}, include:
\begin{enumerate}[label=\roman*),topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item A ``beam window'' on the front outer end cap and an ``excluder'' on the inner endcap.  The purpose of these modifications is to minimize the amount of material upstream of the TPC's active volume along the beam line.  On the original ArgoNeuT cryostat the stainless steel end caps of the cryostat's inner and outer vessels were 3/16'' (4.8 mm) thick. In addition, upstream of the TPC active volume there was a region of uninstrumented liquid argon approximately 15~cm in length. This corresponded to $\sim$ 1.6 radiation lengths ($X_{0}$) of dead material between the outside of the cryostat and the TPC, which would have impeded charged test beam particles prior to their entrance into the active volume.  To mitigate this effect, the 9'' (22.9~cm) diameter beam window located at the center of the outer vessel's front flange was installed along with a blanked 0.4~mm titanium sheet. On the inner vessel's end cap, a hollow concave volume (the ``excluder'') was installed to reduce the amount of liquid argon charged particles would traverse before reaching the active volume of the TPC. With these modificaitons in place, the total material thickness seen by charged particles entering the front face of the LArIAT cryostat is now less than 0.3 $X_{0}$. 
\item A connection for a liquid argon transfer line to the new argon cooling and purification system. This modification consists of an outlet at the bottom of the cryostat with Conflat and ISO flange sealing. 
\item The addition of side port feedthroughs to accomodate signal and high-voltage bias connections for the scintillation light detection system (described in more detail in Section \ref{sec:PhotonSystem}). Both the inner and outer cryostat vessels had their existing side ports modified with CF-flanged apertures to accomplish this.
\end{enumerate}

%$i)$ A ``beam window'' on the front outer end cap and an ``excluder'' on the inner endcap to minimize the amount of material upstream of the TPC's active volume along the beam line; $ii)$ a connection at the base of the cryostat for the argon cooling and purification system; and $iii)$ the addition of a side port feedthrough to accomodate bias and signal connections for the scintillation light detectors.

%On the original ArgoNeuT cryostat the stainless steel end caps of the cryostat's inner and outer vessels were 3/16'' (4.8 mm) thick. In addition, upstream of the TPC active volume there was a region of uninstrumented liquid argon approximately 15~cm in length. This corresponded to $\sim$ 1.6 radiation lengths ($X_{0}$) of dead material between the outside of the cryostat and the TPC, which would have impeded charged test beam particles prior to their entrance into the active volume.  To minimize the effect of this dead region, a 9'' (22.9~cm) diameter beam window located at the center of the outer vessel's front flange was installed along with a blanked 0.4~mm titanium sheet. On the inner vessel's end cap, a hollow concave volume (the ``excluder'') was installed to reduce the amount of liquid argon charged particles would traverse before reaching the active volume of the TPC. With these modificaitons in place, the total material thickness seen by charged particles entering the front face of the LArIAT cryostat is now less than 0.3 $X_{0}$.

%The cryostat vessels were modified to connect a liquid argon transfer line to the new cooling and purification system. This modification consists of an outlet at the bottom of the cryostat with Conflat and ISO flange sealing.

%Finally, both the inner and outer cryostat vessels had their existing side ports modified with CF-flanged apertures for the signal and high-voltage bias feedthroughs for the scintillation light system, described in more detail in Section \ref{sec:PhotonSystem}.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./figures/CryoMods.png}
\caption{Pictures of the modified components of the cryostat. $1)$ The addition of an outlet to the bottom of the cryostat to allow connections to the purification system; $2)$ The ``beam-window'' on the outer endcap and the concave inner surface of the inner endcap (referred to as the excluder) to reduce the amount of material through which beam particles must travel before entering the TPC; $3)$ The modified side port for the LArIAT light collection system.}
\label{fig:LArIATCryoMods}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}{Liquid Argon System}\label{sec:LArCryoSystem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
LArIAT is supplied with liquid argon from a commercial dewar positioned outside of the experimental enclosure.  Liquid argon is delivered by a vendor with a specified maximum contamination of 2 parts per million (ppm) oxygen, 3.5~ppm water, and 10~ppm nitrogen. Oxygen and water contamination is detrimental to the ability of the ionization electrons to drift through the volume, as free electrons readily attach to these molecules. Nitrogen contamination is detrimental to the collection of scintillation light.  The level of these contaminants in the delivered argon is determined using a suite of commercial gas analyzers.  In practice, the delivered argon has much less than 1~ppm of all these contaminants.  Even such apparently low levels of contamination are too large to effectively drift ionization electrons, so filtration of the argon is required to achieve oxygen and water contamination at the level of 100 parts per trillion (ppt) or better. %{\bf 100 ppt is sufficient for a 3 ms lifetime, I think LArIAT has less than that}.

The argon is delivered from the commercial dewar to the cryostat through 2.54~cm diameter schedule 10 stainless steel piping.  The piping was insulated with 20.32~cm of polyurethane foam by the manufacturer.  The piping was cleaned to remove oil and grease before being welded into the system. The argon then passes through LArIAT's argon filtration system which is based on the Liquid Argon Purity Demonstrator (LAPD)~\cite{LAPD} design. The purification system consists of a single 77~liter filter which is filled halfway with a 4A molecular sieve supplied by Sigma-Aldrich~\cite{sigma-aldrich} that primarily removes water contamination but can also remove small amounts of nitrogen and oxygen. The remaining volume of the filter contains BASF~CU-0226~S, a highly dispersed copper oxide impregnated on a high surface area alumina, to remove oxygen~\cite{basf} and to a lesser extent, water.  The filter is insulated with a vacuum jacket and aluminum radiation shields.  The filter media are regenerated in place using heated gas, as was done for LAPD. The filter media are very efficient at removing oxygen and water and the argon is pure enough after a single pass through the media to allow several millisecond electron drift lifetimes in the TPC.

From the filter the argon is directed into the inner cryostat via a liquid feedthrough on the top of the cryostat. The argon level, temperatures, and pressures are continuously monitored during operation both in the commercial dewar supplying the argon as well as the levels inside the cryostat, as shown on the top of Figure \ref{fig:LArIATCryoMonitor}. The argon in the cryostat is allowed to boil and vent to the atmosphere during operation and the argon level is monitored via the level probes. Flow of argon into the cryostat is enabled whenever the liquid level goes below a predetermined value to ensure that the TPC high voltage feedthrough and cold electronics are always submerged. During normal operations, the liquid level inside the cryostat is replenished several times per day, as can be seen by the cycle of the liquid level and valve positions shown at the bottom of Figure \ref{fig:LArIATCryoMonitor}

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./figures/CryoMonitor.png}
\includegraphics[scale=0.34]{./figures/CryoMonitor2.png}
\caption{\emph{(top)} Screenshot of the LArIAT cyrosystem monitoring page showing the levels of the argon both inside the cryostat and in the supply dewar as well as the monitored levels plotted over a twenty-four hour period. \emph{(bottom)} Plots showing the liquid argon level inside the cryostat as well as the corresponding liquid valve which allows argon to flow into the cryostat and the level drops due to boiling. The frequency of the typical fill/vent cycle can be seen with the typical time between fills being slightly more than 3 hours.}
\label{fig:LArIATCryoMonitor}
\end{figure}

The temperature of the argon inside the cryostat can be determined through direct use of temperature probes deployed at the bottom, middle, and top of the cryostat (listed as TE213A, TE314A, and TE212A in Figure \ref{fig:LArIATCryoMonitor} respectively). This can be crossed check using the pressure in the cryostat gas volume and extrapoloting this to the center of the liquid volume. The pressure at the surface of the liquid argon is maintained by the cryosystem at $\sim$20~psi $\pm$.0.4 psi.

In order to determine the temperature inside the TPC, we measure the pressure in the cryostat gas volume and calculate the pressure at the center of the TPC. From this pressure and the boiling point curve of argon, we calculate the temperature. The pressure at the surface of the liquid argon is maintained by the cryosystem at $\sim$20~psi as shown in Figure \ref{fig:pressure} for a period of 13 days with an average pressure of 20.0 $\pm$.0.4 psi. If we consider approximately 40 cm of argon from the ulage surface to the center of the TPC this would give the pressure there of $\sim$20.8 psi, which according to the Reference \cite{} corresponds to a temperature of 90.7 K. This is consistent with the readings given of the temperature probes, shown in Table \ref{tab:temp}. This cross-check both provides a basis for the electron mobility calculation used when calibrating the drift speed, as is discussed in Section \ref{}, as well as providing confidence in the monitoring tools.

\begin{table}[h!]
\centering
\caption{Average temperatures measured at the top, middle and bottom in the LArIAT cryostat.}
\label{tab:temp}
\begin{tabular}{|c|c|c|}
\hline
Top Probe Temp (TE212A) & Middle Probe Temp (TE214A)   & Bottom Probe Temp (TE213A)  \\ \hline
91.7 $\pm$ 0.7 K &  91.8 $\pm$ 0.7 K                   & 93.3 $\pm$ 2.7 K       \\ \hline
\end{tabular}
\end{table}

\end{subsubsection}
The Liquid Argon Time Projection Chamber (LArTPC) can be broken down into three major subcomponents: $1)$ The high voltage system which provides the drift field voltage; $2)$ the cathode and field cage which steps down the high voltage through a network of voltage-dividing resistors to form a uniform electric field for charges to drift within; and $3)$ the wire planes which provide the charge sensitive readout for the detector. Here we describe each of the subcomponents which make up the LArIAT LArTPC.

>>>>

The Liquid Argon Time Projection Chamber (LArTPC) can be broken down into three major subcomponents: $1)$ The high voltage system which provides the drift field voltage; $2)$ the cathode and field cage which steps down the high voltage through a network of voltage-dividing resistors to form a uniform electric field for charges to drift within; and $3)$ the wire planes which provide the charge sensitive readout for the detector. Here we describe each of the subcomponents which make up the LArIAT LArTPC.
